Numerical Investigation of Viscous Flow Instabilities in Multiphase Heterogeneous Porous Media

### 2018-04-18 Papers/ViscousInstabilities/article_figure1.tex
update

%%%
%%% FIGURE XXXXXX
%%%
  \begin{figure}[ht]
  \vbox{\vspace{-1.cm}
      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_D0b.pdf} 
            \includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_D350b.pdf}}
      \vspace{-.1cm}\hbox{\hspace{2.cm}(a) t=0.00s \hspace{4cm} (f) t= 0.35s}\vspace{-.1cm}
      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_D100b.pdf} 
            \includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_D700b.pdf}}
      \vspace{-.1cm}\hbox{\hspace{2.cm}(b) t=0.10s \hspace{4cm} (g) t= 0.70s}\vspace{-.1cm}
      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_D150b.pdf} 
            \includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_D1000b.pdf}}
      \vspace{-.1cm}\hbox{\hspace{2.cm}(c) t=0.15s \hspace{4cm} (h) t= 1.00s}\vspace{-.1cm}
      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_D200b.pdf} 
            \includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_D1500b.pdf}}
      \vspace{-.1cm}\hbox{\hspace{2.cm}(d) t=0.20s \hspace{4cm} (i) t= 1.50s}\vspace{-.1cm}
      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_D250b.pdf}}
      \vspace{-.1cm}\hbox{\hspace{2.cm}(e) t=0.25s}\vspace{-.1cm}}
\caption{Impact of mesh resolution on capturing flow instabilities: snapshots of saturation field through 1.50 seconds of numerical simulation performed with fixed mesh (of 13068 elements) and {\it VR}=10.}
\label{fig:5regions_fixedmesh}
\end{figure}
\clearpage

%%%
%%% FIGURE XXXXXX
%%%
  \begin{figure}[ht]
  \vbox{\vspace{-2.cm}
      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D0b.pdf} 
            \includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D250b.pdf}}
      \vspace{-.1cm}\hbox{\hspace{2.cm}(a) t=0.00s \hspace{4cm} (f) t= 0.35s}\vspace{-.1cm}
      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D100b.pdf} 
            \includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D700b.pdf}}
      \vspace{-.1cm}\hbox{\hspace{2.cm}(b) t=0.10s \hspace{4cm} (g) t= 0.70s}\vspace{-.1cm}
      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D150b.pdf} 
            \includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D1000b.pdf}}
      \vspace{-.1cm}\hbox{\hspace{2.cm}(c) t=0.15s \hspace{4cm} (h) t= 1.00s}\vspace{-.1cm}
      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D200b.pdf} 
            \includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D1500b.pdf}}
      \vspace{-.1cm}\hbox{\hspace{2.cm}(d) t=0.20s \hspace{4cm} (i) t= 1.50s}\vspace{-.1cm}
      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D350b.pdf}}
      \vspace{-.1cm}\hbox{\hspace{2.cm}(e) t=0.25s}\vspace{-.1cm}}
\caption{Impact of mesh resolution on capturing flow instabilities: snapshots of saturation field through 1.50 seconds of numerical simulation performed with adaptive mesh and {\it VR}=10.}
\label{fig:5regions_adaptmesh}
\end{figure}
\clearpage

>>>>

%%%
%%% FIGURE XXXXXX
%%%
  \begin{figure}[ht]
  \vbox{\vspace{-1.cm}
      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_D0b.pdf} 
            \includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_D250b.pdf}}
      \vspace{-.1cm}\hbox{\hspace{2.cm}(a) t=0.00s \hspace{4cm} (f) t= 0.35s}\vspace{-.1cm}
      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_D100b.pdf} 
            \includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_D700b.pdf}}
      \vspace{-.1cm}\hbox{\hspace{2.cm}(b) t=0.10s \hspace{4cm} (g) t= 0.70s}\vspace{-.1cm}
      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_D150b.pdf} 
            \includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_D1000b.pdf}}
      \vspace{-.1cm}\hbox{\hspace{2.cm}(c) t=0.15s \hspace{4cm} (h) t= 1.00s}\vspace{-.1cm}
      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_D200b.pdf} 
            \includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_D1500b.pdf}}
      \vspace{-.1cm}\hbox{\hspace{2.cm}(d) t=0.20s \hspace{4cm} (i) t= 1.50s}\vspace{-.1cm}
      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_D350b.pdf}}
      \vspace{-.1cm}\hbox{\hspace{2.cm}(e) t=0.25s}\vspace{-.1cm}}
\caption{Impact of mesh resolution on capturing flow instabilities: snapshots of saturation field through 1.50 seconds of numerical simulation performed with fixed mesh (of 13068 elements) and {\it VR}=10.}
\label{fig:5regions_fixedmesh}
\end{figure}
\clearpage

%%%
%%% FIGURE XXXXXX
%%%
  \begin{figure}[ht]
  \vbox{\vspace{-2.cm}
      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D0b.pdf} 
            \includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D350b.pdf}}
      \vspace{-.1cm}\hbox{\hspace{2.cm}(a) t=0.00s \hspace{4cm} (f) t= 0.35s}\vspace{-.1cm}
      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D100b.pdf} 
            \includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D700b.pdf}}
      \vspace{-.1cm}\hbox{\hspace{2.cm}(b) t=0.10s \hspace{4cm} (g) t= 0.70s}\vspace{-.1cm}
      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D150b.pdf} 
            \includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D1000b.pdf}}
      \vspace{-.1cm}\hbox{\hspace{2.cm}(c) t=0.15s \hspace{4cm} (h) t= 1.00s}\vspace{-.1cm}
      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D200b.pdf} 
            \includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D1500b.pdf}}
      \vspace{-.1cm}\hbox{\hspace{2.cm}(d) t=0.20s \hspace{4cm} (i) t= 1.50s}\vspace{-.1cm}
      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D250b.pdf}}
      \vspace{-.1cm}\hbox{\hspace{2.cm}(e) t=0.25s}\vspace{-.1cm}}
\caption{Impact of mesh resolution on capturing flow instabilities: snapshots of saturation field through 1.50 seconds of numerical simulation performed with adaptive mesh and {\it VR}=10.}
\label{fig:5regions_adaptmesh}
\end{figure}
\clearpage
